Data Preparation

### 2023-03-23 x_data-crunching.qmd
initial use of sfnetwork for blending thr point in linestring/sequence of lat-long nodes

```{r}
#| message: false
library(tidyverse)
library(sf)

@@

@@

>>>>

```{r}
#| message: false
library(tidyverse)
library(sf)
library(patchwork)

@@

viz_check_vertical <- function(.trj){
  plt <- .trj |> 
    ggplot() +
    geom_point(aes(x = TIME, y = ALT_B))
  return(plt)
}

@@

landing runway assignment

```{r}
source("~/RProjects/paper-2023-ICNS/R/trj_landing_runway.R")

# test for one
arr_rwy <- arr_trjs |> filter(UID == "00b1f9-0") |> assign_landing_runway()
arr_rwy

arr_rwys <- arr_trjs |> assign_landing_runway()
arr_rwys
```

```{r}
arr_rwys |> ggplot() + geom_histogram(aes(x = TRUST), bindwidth = 2)
```

# check for some fringe cases

```{r}
fringe_picks <-  arr_rwys |> filter(between(TRUST, 0.4,0.7))

viz_check_DAO(arr_trjs |> filter(UID %in% fringe_picks$UID)) + facet_wrap(.~ UID)
```

Potential to remove = no landing with TRUST < 0.7

* assign landing runway & landing time

do for one/some

> arr_rwys
# A tibble: 733 × 6
# Groups:   UID [733]
   UID      REF       N   TOT TRUST COMMENT                                                      
   <chr>    <chr> <int> <int> <dbl> <chr>                                                        
 1 00b1f9-0 27L      13    16 0.812 landing runway: 27L trust-Level (hits: 13): 0.8125           
 2 01013c-0 27L      11    14 0.786 landing runway: 27L trust-Level (hits: 11): 0.785714285714286
 3 0101bb-0 27R      12    15 0.8   landing runway: 27R trust-Level (hits: 12): 0.8              
 4 0200cb-0 27R      12    15 0.8   landing runway: 27R trust-Level (hits: 12): 0.8              
 5 04014c-0 27L      12    15 0.8   landing runway: 27L trust-Level (hits: 12): 0.8              
 6 04c15b-0 27R      11    14 0.786 landing runway: 27R trust-Level (hits: 11): 0.785714285714286
 7 06a0e6-0 27R      12    15 0.8   landing runway: 27R trust-Level (hits: 12): 0.8              
 8 06a11f-0 27R      12    15 0.8   landing runway: 27R trust-Level (hits: 12): 0.8              
 9 06a144-0 27L      13    16 0.812 landing runway: 27L trust-Level (hits: 13): 0.8125           
10 06a149-0 27L      13    16 0.812 landing runway: 27L trust-Level (hits: 13): 0.8125

```{r}
arr_trjs |> filter(UID %in% c("00b1f9-0","01013c-0","0101bb-0","0200cb-0")) |> 
  viz_check_DAO() + facet_wrap(.~UID)
```

```{r}
arr_trjs |> filter(UID %in% c("00b1f9-0")) |> 
  ggplot(
    aes(  x = TIME
        , y = ALT_B
        , color = between(ALT_B, arp_egll$ELEV + 100, arp_egll$ELEV + 1000)
        )
    ) + 
  geom_point() + labs(color = "Approach")
```

```{r}
source("~/RProjects/paper-2023-ICNS/R/cast_sf_network.R")

arp  <- arp_egll
rwys <- rwys_egll

final <- arr_trjs |> filter(UID %in% c("00b1f9-0")) |>
  filter(ALT_B < arp$ELEV + 2000)

ldg_rwy <- final |> assign_landing_runway(.arp = arp) |> 
  inner_join(rwys, by = "REF")
my_thr  <- ldg_rwy |> select(UID, REF, LAT, LON, COMMENT) |> cast_latlon_to_pts(.drop_coord = FALSE)

final_sfn <- final |> cast_latLon_to_sfnet()
# blend crossing in network
# c.f. https://luukvdmeer.github.io/sfnetworks/reference/st_network_blend.html
# blend points with a tolerance.
# tol = units::set_units(50, "m")
final_sfn <- final_sfn %>%
    sfnetworks::st_network_blend(my_thr |> select(REF, geometry)) #, tolerance = tol)

viz_check_vertical(final) + viz_check_DAO(final)
```

check for blended point
final_sfn |> activate("nodes") |> filter(is.na(TIME)) |> select(TIME, ICAO24, LAT, LON, ALT_B, geometry)

point is injected, need to fill details, e.g. TIME
then extract nodes ~ enriched sequence of final points (maybe use sequence number)

NEXT-NEXT
* calculate characteristics
  + time-to-go
  + distance-to-go
  + crossings (e.g for ASMA)
